Automated Formal Synthesis of Digital Controllers for State-Space Physical Plants

### 2017-01-24 cav2017/cav2017.tex
added contributions

\begin{abstract}
This work presents a sound and automated approach to synthesise 
digital feedback control architectures for physical plants represented 
as linear, time invariant models. Models are encompassed by dynamical 
equations with inputs, evolving over a continuous state space describing 
the evolution of the physical variables of the system.  The approach is divided 
in two main parts, brought together by a counter-example guided inductive 
synthesis (CEGIS) loop, as follows. First, we devise a static feedback controller 
that stabilises the system; then, we verify its potential safety by means of either 
of the following approaches: forward reachability analysis via unfolding of the dynamics, 
or invariant set generation via abstract acceleration;  
further, if the above step fails, we loop back and invoke a CEGIS call 
to seek alternative stabilising feedbacks, benefiting from the obtained counter-examples 
to safety.

The approach is proven sound by accounting for errors due to the digitalisation of signals that are manipulated by the controller block.  
The proposed synthesis approaches and a developed tool are evaluated considering 
a set of intricate physical plant models taken from the digital control literature.
\keywords{
State-space dynamical models of physical systems; 
Digital controllers; 
Analogue-to-digital converters; 
Time sampling; 
quantization; 
Fixed-point arithmetic; 
CEGIS; 
safety requirements. 
}
\end{abstract}

@@

We describe and evaluate two approaches for synthesizing digital controllers 
for state-space physical plants. Both approaches consider a counterexample 
guided inductive synthesis (CEGIS) loop. In the first approach, 
we devise a digital controller that stabilises the system; then, we verify its 
potential safety by unfolding the dynamics of the system and checking for 
a completeness threshold. \textcolor{red}{Dario: Can you please briefly explain your approach?
In the second approach,...}

\textcolor{red}{we have to connect both paragraphs...}

To this end, we formalise the notion of solution generalisation for
Counter-Example Guided Inductive Synthesis (CEGIS), which makes use 
of abstraction refinement in order to achieve scalability.
This strategy enables the inductive generalisation engine inside CEGIS
to look for candidate solutions in a reduced solution space.

\addtodo{We have to summarise our main contributions here}

>>>>

\begin{abstract}
This work presents a sound and automated approach to synthesise 
digital feedback control architectures for physical plants represented 
as linear, time invariant models. Models are encompassed by dynamical 
equations with inputs, evolving over a continuous state space describing 
the evolution of the physical variables of the system.  The approach is divided 
in two main parts, brought together by a counter-example guided inductive 
synthesis (CEGIS) loop, as follows. First, we devise a static feedback controller 
that stabilises the system; then, we verify its potential safety by means of either 
of the following approaches: forward reachability analysis via unfolding of the dynamics, 
or invariant set generation via abstract acceleration;  
further, if the above step fails, we loop back and invoke a CEGIS call 
to seek alternative stabilising feedbacks, benefiting from the obtained counter-examples 
to safety. The approach is proven sound by accounting for errors due to the digitalisation 
of signals that are manipulated by the controller block.  
The proposed synthesis approaches and a developed tool are evaluated considering 
a set of intricate physical plant models taken from the digital control literature.
\keywords{
State-space dynamical models of physical systems; 
Digital controllers; 
Analogue-to-digital converters; 
Time sampling; 
quantization; 
Fixed-point arithmetic; 
CEGIS; 
safety requirements. 
}
\end{abstract}

@@

We describe and evaluate two approaches for synthesizing digital controllers 
for state-space physical plants. Both approaches consider a counterexample 
guided inductive synthesis (CEGIS) loop. In the first approach, 
we devise a digital controller that stabilises the system; then, we verify its 
potential safety by unfolding the dynamics of the system and checking for 
a completeness threshold. In the second approach, we employ abstract acceleration
to accelerate the dynamics forward instead of symbolically unwinding the 
transition relation~\cite{cattaruzza2015unbounded}.

%\textcolor{red}{we have to connect both paragraphs...}

%To this end, we formalise the notion of solution generalisation for
%Counter-Example Guided Inductive Synthesis (CEGIS), which makes use 
%of abstraction refinement in order to achieve scalability.
%This strategy enables the inductive generalisation engine inside CEGIS
%to look for candidate solutions in a reduced solution space.

In summary, this paper makes the following original contributions.
%
\begin{itemize}

\item We design and implement two approaches to synthesize 
  digital feedback control architectures for physical plants, 
	considering dynamical equations with inputs that evolves over 
	a continuous state space. In both approaches, we apply CEGIS to 
	devise a digital controller that stabilizes the system and we then
	we verify safety by means of either forward reachability analysis 
	via dynamics unfolding or invariant set generation via 
	abstract acceleration.

\item We provide experimental results showing that our approaches
  are able to efficiently synthesize stable and safe controllers 
	for a set of intricate physical plant models taken from the digital 
	control literature: the median runtime for our benchmark
  set is \textcolor{red}{$XXX$}s, i.e., most controllers can be synthesized in less
  than \textcolor{red}{$XXX$} seconds.

\end{itemize}
